Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2022-12-21 manuscript/manuscript.tex
Add reference energy/density table

Setting the reference density according to the water model used in your simulation is important to get correct results.
Densities of typical water models can be found in the \software{cpptraj} manual.
For other models, the density should be computed from a pure water simulation.

@@

To faciliate an accessible way to interact with your GIST data, we recommend using the gisttools library for python3. Open the GIST output with gisttools:
\begin{lstlisting}[style=python]
	from gisttools.gist import load_gist_file
	import matplotlib.pyplot as plt
	gist = load_gist_file(
	"gist.dat", struct="solute-centered.pdb",  eww_ref=-9.539)
	print(f'n_frames = {gist.n_frames}')
	print(f'rho0 = {gist.rho0}')
\end{lstlisting}
All information from the output file is now accessible through the gist object. 
If the number of frames of the simulation ($n_frames$) and the reference density (rho0) are not provided, they are automatically detected from the GIST data. 
We will discuss a way to similarly detect the reference energy of the solvent-solvent energy Eww in the advanced section.

@@

\begin{lstlisting}[style=python]
	gist.save_dx('A_dens', ')
	with open(fname) as f:
		print([next(f) for x in range(10)])
\end{lstlisting}

>>>>

Setting the reference density $\rho_0$ according to the solvent model used in your simulation is important to get correct results. You will also want to reference the bulk mean solvent-solvent enthalpy $E_{ww}$ correctly, though we will show ways to do this differently in a later section of the tutorial.

Densities of typical water models can be found in the \software{cpptraj} manual.
We also provide the densities for water models commonly used with AMBER forcefields in table \ref{tab:ref_densities}. These densities were calculated from 1$\mu$s MD simulations. Pressure was kept constant at 1 bar with the Berendsen barostat and the water box was prepared with tleap to a size of 100$\cdot$100$\cdot$100\AA before pressure equilibration. The temperature was kept constant at 300 K with the Langevin thermostat.
\begin{table}[h]
	\caption{Reference density $\rho_0$ and mean water-water energy $E_{ww, norm}$ for various water models from NpT simulations at 300K/1bar.}\label{tab:ref_densities}
	\small
	\begin{tabularx}{\columnwidth}{@{}lrr@{}}
		\toprule
		Water Model       & $\rho_0$ /\AA$^{-3}$ & $E_{ww, norm}$ /$kcal\cdot mol^{-1} \cdot water^{-1}$  \\
		\midrule
		TIP3P    & 0.0329 & -9.533   \\
		TIP3PFB  & 0.0334 & -11.369  \\
		TIP4P    & 0.0332 & -9.856   \\
		TIP4P/Ew & 0.0332 & -11.036  \\
		TIP5P    & 0.0329 & -9.596   \\
		SPC/E    & 0.0333 & -11.123  \\
		OPC      & XXXX   & XXXX     \\
		OPC3     & XXXX   & XXXX     \\
		POL3     & XXXX   & XXXX     \\
		\bottomrule
	\end{tabularx}
\end{table}
If your simulation settings diverge significantly from the above setting or for other solvent models not listed either here or in the \software{cpptraj} manual, the density should be computed from a pure solvent simulation beforehand.

@@

To faciliate an accessible way to interact with your GIST data, we recommend using the gisttools library for python3. Open the GIST output with gisttools:
\begin{lstlisting}[style=python]
	from gisttools.gist import load_gist_file
	import matplotlib.pyplot as plt
	gist = load_gist_file(
	"gist.dat", struct="solute-centered.pdb",  eww_ref=-9.539)
	print(f'n_frames = {gist.n_frames}')
	print(f'rho0 = {gist.rho0}')
\end{lstlisting}
All information from the output file is now accessible through the gist object. 
If the number of frames of the simulation (n\_frames) and the reference density (rho0) are not provided, they are automatically detected from the GIST data. 
We will discuss a way to similarly detect the reference energy of the solvent-solvent energy Eww in the advanced section.

@@

\begin{lstlisting}[style=python]
	gist.save_dx('A_dens','A.dx')
	with open('A.dx') as f:
		print([next(f) for x in range(10)])
\end{lstlisting}
